An Image-based method for phase estimation, gating and temporal super-resolution of \\cardiac ultrasound

### 2017-02-24 paper155.tex
Correct error -- referenced wrong figure in introduction

\vskip0.5ex
\noindent
\textbf{Contributions.} In this paper, we present a novel method that estimates the instantaneous cardiac and respiratory phases directly from the cardiac ultrasound video(Figure~\ref{fig:phase_estimation}). We also present a robust non-parametric regression technique for gating out respiratory frames and a novel kernel regression model for reconstructing images at any cardiac phase to facilitate temporal super-resolution.

>>>>

\vskip0.5ex
\noindent
\textbf{Contributions.} In this paper, we present a novel method that estimates the instantaneous cardiac and respiratory phases directly from the cardiac ultrasound video(Figure~\ref{fig:instaphase_vs_ecg}). We also present a robust non-parametric regression technique for gating out respiratory frames and a novel kernel regression model for reconstructing images at any cardiac phase to facilitate temporal super-resolution.
